Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
Clement's corrections

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
Univ. de Paris, F-75013 Paris, France
\and
to fill!
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
}

@@

\TODO[Clément]{We haven't defined winning strategies}
\begin{theorem}
  In the Hydra game, every strategy is a winning strategy for Hercules. \label{kp:thm1}
\end{theorem}

@@

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good theme for a commented library~\cite{HydraBattles} of formal proofs written for the \textit{Coq} proof assistant~\cite{Coq}.

Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook} (PDF document of over 280 pages). Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\ref{fig:Ex42E0} and \ref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$. The first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}.

>>>>

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
to fill!
\and
to fill!
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
to fill!
 }

@@

\begin{theorem}
  n the Hydra game, Hercules eventually wins, whichever the strategy of both players :
  choice of a head to chop off, choice of the number of copies. 
 \label{kp:thm1}
\end{theorem}

@@

The contrast between the simplicity of the statements above and the complexity of their proofs convinced us that it is a good thema for a commented library~\cite{HydraBattles} of formal proofs written for the \textit{Coq} proof assistant~\cite{Coq}.

Complex formalisations and proofs are explained in an
  electronic book~\cite{HydraBook}. Whenever various reasonable choices exist, we try to present and compare the alternatives.
  For instance, Figures~\ref{fig:Ex42E0} and \ref{fig:Ex42-schutte} show two radically different proofs of the equality
  $\omega+42+\omega^2=\omega^2$. The first one is a simple proof by computation, the second one shows how this equality
  is a consequence of the axioms of the set-theoretic model  by Kurt Schütte~\cite{schutte}.
